Bird beak's elaboration and innovation

### 2022-07-15 Analysis/04-Figure3_with_ellipse_scalling_and_8D_histograms.Rmd
added passeriformes

## Plotting the aligned and scale ellipses for the superorders
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(superorder_shapespace, ellipses = mean,
           col = match.col(superorder_shapespace, tip_colours_super_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(1, length(tip_colours_super_orders)), 3),
           add = TRUE)

@@

par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(order_shapespace, ellipses = mean,
           col = match.col(order_shapespace, tip_colours_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(0.5, length(tip_colours_orders)), 3),
           add = TRUE)

@@

```{r}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_passeriformes.pdf", height = box_size*7, width = box_size*10)

## Global window
lay_mat_family <- rbind(
        matrix(c(1,1, 2:9), ncol = 10, nrow = 1), # line 1
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1), # line 2
        matrix(c(1,1, 18:25), ncol = 10, nrow = 1), # line 3
        matrix(c(26:35), ncol = 10, nrow = 1), # line 4
        matrix(c(36:45), ncol = 10, nrow = 1), # line 5
        matrix(c(46:47, rep(-13,8)), ncol = 10, nrow = 1) # line 6
    )
lay_mat_sub <- rbind(
        matrix(c(1,1, 2:9, c(1,1), 10:13, rep(0, 4)), ncol = 10, nrow = 2, byrow = TRUE) # line 7
    )
heights_vals <- rep(1, 8)
widths_vals <- rep(c(1, 1/3), 5)
layout_matrix <- layout(rbind(lay_mat_sub, (lay_mat_family+13)), widths = widths_vals, heights = heights_vals, respect = TRUE)
# layout.show(layout_matrix)

@@

## Plotting the aligned and scale ellipses for the superorders
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(suborder_shapespace, ellipses = mean,
           col = match.col(suborder_shapespace, tip_colours_suborders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(1, length(tip_colours_suborders)), 3),
           add = TRUE, n = 50)

par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(family_shapespace, ellipses = mean,
           col = match.col(family_shapespace, tip_colours_families),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(0.5, length(tip_colours_families)), 3),
           add = TRUE, n =50)
dev.off()

>>>>

## Plotting the aligned and scale ellipses for the superorders
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(superorder_shapespace, ellipses = mean,
           col = match.col(superorder_shapespace, tip_colours_super_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(1, length(tip_colours_super_orders)), 3),
           add = TRUE, n = 100)

@@

par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(order_shapespace, ellipses = mean,
           col = match.col(order_shapespace, tip_colours_orders),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(0.5, length(tip_colours_orders)), 3),
           add = TRUE, n = 100)

@@

```{r}
box_size <- 1.5
pdf(file = "../Manuscript/Figures/Figure3_passeriformes.pdf", height = box_size*9, width = box_size*10)

## Global window
x <- 61
lay_mat_sub <- rbind(
        matrix(c(1,1, rep(x, 3), 0, 2:5), ncol = 10, nrow = 1), # line 7
        matrix(c(1,1, rep(x, 3), 0, 6:9), ncol = 10, nrow = 1), # line 8
        matrix(c(x+2,x+2, 10:13, rep(x+3, 4)), ncol = 10, nrow = 1) # line 8
    )
y <- x - 13
lay_mat_family <- rbind(
        matrix(c(1,1, rep(y+1, 3), y+4, 2:5), ncol = 10, nrow = 1), 
        matrix(c(1,1, rep(y+1, 3), y+4, 6:9), ncol = 10, nrow = 1), 
        matrix(c(1,1, 10:17), ncol = 10, nrow = 1),
        matrix(c(18:27), ncol = 10, nrow = 1),
        matrix(c(28:37), ncol = 10, nrow = 1), 
        matrix(c(38:47), ncol = 10, nrow = 1)
    )
heights_vals <- rep(1, 8)
widths_vals <- rep(c(1, 1/3), 5)
layout_matrix <- layout(rbind(lay_mat_sub, (lay_mat_family+13)), widths = widths_vals, heights = heights_vals, respect = TRUE)
# layout.show(layout_matrix)

@@

## Plotting the aligned and scale ellipses for the superorders
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(suborder_shapespace, ellipses = mean,
           col = match.col(suborder_shapespace, tip_colours_passeriformes_suborder),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(1, length(tip_colours_passeriformes_suborder)), 3),
           add = TRUE, n = 100)

## PLOTTING THE ORDERS
par(bty = "n")
lims <- c(-1/3, 1/3) # c(-1.25, 1.25)
plot(NULL, xlim = lims, ylim = lims, xaxt = "n", yaxt = "n", xlab = "n", ylab = "n")
abline(v = 0, col = "grey", lwd = 0.5)
abline(h = 0, col = "grey", lwd = 0.5)
covar.plot(family_shapespace, ellipses = mean,
           col = match.col(family_shapespace, tip_colours_passeriformes_family),
           legend = FALSE, points = FALSE, scale = "phylogeny",
           lines.lwd = c(rep(0.5, length(tip_colours_passeriformes_family)), 3),
           add = TRUE, n = 100)
dev.off()
